|

### 2022-03-27 03-Chp-Systematic-Review-Methods.Rmd
Define rare outcome

The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc.) are not directly interchangeable in the context of systematic review.  As such, different reported effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019] However if the outcome is rare, as is the case for dementia outcomes, the estimated odds, risk and hazard ratios will approximate each other.[@vanderweele2020] As such, I did not stratify the analyses by reported effect measure.

>>>>

The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc.) are not directly interchangeable in the context of systematic review.  As such, different reported effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019] However if the outcome is rare [(<10%)]{.correction}, as is the case for dementia outcomes, the estimated odds, risk and hazard ratios will approximate each other.[@vanderweele2020] As such, I did not stratify the analyses by reported effect measure.
